\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multicol}
\textheight=10in
\pagestyle{empty}
%\raggedbottom
\raggedright
\raggedcolumns

%  \renewcommand{\encodingdefault}{cg}
  %\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME
\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1}   #2 \end{verse}  }
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder}
\newcommand{\employer}[3]{{ \textbf{#1} \\ \underline{\textbf{\emph{#3}}} \hfill #2\\  }}
\newcommand{\contact}[3]{
\vspace*{-8pt}
\begin{center}
{\LARGE \scshape {#1}}\\
#2 \lineunder 
#3
\end{center}
\vspace*{-8pt}
}
\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}}
\newcommand{\schoolwithcourses}[4]{
\textbf{#1} \\
#2 \hfill #3 \\
#4\\ 
\underline{Selected Coursework:}\\

}
\newcommand{\school}[4]{
 \textbf{#1} #2 $\bullet$ #3\\ 
#4 \\
}
% END RESUME DEFINITIONS

\begin{document}

\small
\smallskip
\vspace*{-44pt}

\contact{Alex Poms}
{San Mateo, California 94402}
{(650) 787-7255 $\bullet$ alexpoms@gmail.com}

\begin{center}

\end{center}

\header{Education}

\schoolwithcourses{University of California, Davis}{Bachelor of
  Science in Computer Science}{Expected Graduation June 2014}
{Cumulative GPA: 3.50/4.00}
\vspace*{-8pt}
\begin{multicols}{2}
\begin{itemize} \itemsep0em
\item Data Structures
\item Machine Assembly Programming
\item Operating Systems
\item Programming language theory
\item Interactive Visualization
\item Compiler design
\end{itemize}
\end{multicols}

\header{Work History}
\employer{Microsoft}{June - September 2013}{Software Development
  Intern in Test}
\begin{achievements}
\item Researched, designed, and built a self-contained internal test
  reproduction and diagnosis tool for Direct2D.
\item Set in place clear UI principles and iterated on code
  architecture to ensure that maintainers require minimal system
  knowledge to implement new features.
\item Took on responsibilities which ranged across the Software
  Developer, Program Manager, and Software Developer in Test roles.
\end{achievements}

\employer{Intel}{June - September 2012}{Graphics Software Validation
  Engineer Intern}
\begin{achievements}
\item Utilized fuzzing frameworks to discover and accurately diagnose
  security exploits in graphics driver software
\item Programmed and deployed custom test suites to automated systems that run on a regular cadence.
\item Sought collaboration with different members within the the
  organization in order to accelerate test production.
\item Built in-house tools to accelerate manual tuning and testing.
\end{achievements}

\employer{Dr. Zhendong Su}{September 2012 - June 2013} {Undergraduate
  Research Assistant}
\begin{achievements}
\item Constructed software to identify geometric patterns in
  images and form meaningful representations of those patterns.
\item Researched innovative approaches to online education that
  focus on adaptive, personalized learning through student modelling.
\item Collaborated with a post-doc and foreign exchange student to distribute work.
\item Researched and implemented relevant computer vision algorithms.
  modeling. 
\end{achievements}

\header{Skills}
\begin{multicols}{2}
  
\underline{Languages}
\begin{itemize}\itemsep0em
\begin{multicols}{2}
\item C++
\item C\#
\item Java
\item Clojure
\item Python
\item Javascript
\item CSS/HTML5
\end{multicols}
\end{itemize}
\columnbreak

\underline{Technologies}
\begin{itemize}\itemsep0em
\begin{multicols}{2}
\item DirectX
\item OpenGL
\item Peach
\item Compojure
\item Ring
\item SaltStack
\item WPF
\item XNA
\end{multicols}
\end{itemize}
\end{multicols}

\vspace*{-8pt}
\header{Honors and Awards}
\employer{Microsoft Imaginecup}{2012}{US Game Design Finalist}
\begin{achievements}
\item Gave quick pitches and long presentations on all aspects of the
  product, including game-play, business, technical aspects and future plans.
\item Worked closely with a multi-disciplinary team to create an
  experience that brings to light the complicated issues involved in
  environmental sustainability.
\item Built for Windows Phone 7 using the XNA framework.
\end{achievements}

\header{Leadership Positions}
\employer{Davis Computer Science Club}{Fall 2013 - Present}{President}
\begin{achievements}
\item Motivated officers by establishing a clear vision for redefining
  Computer Science for students at UC Davis
\item Worked with industry representatives and Davis representatives
  to coordinate events and connect companies to club members.
\item Attracted innovative speakers to give talks at club meetings.
\end{achievements}


\end{document}
